Predicting sales of newly published books

### 2015-09-17 paper.tex
Añadiendo descripción de SOM
Y un par de citas

\textbf{FALTA EXPLICAR EN UN PAR DE PÁRRAFOS QUÉ ES EL SOM DE KOHONEN.}

>>>>

SOM is a feedforward neural network \cite{Haykin98_NNC} that uses an unsupervised training algorithm and which, through a process called self-organization, configures the output units into a topological representation of the original data. It tries to imitate the self-organization done in the sensory cortex of the human brain, where neighbouring neurons are activated by similar stimulus. SOM belongs to a general class of neural network methods, which are non-linear regression techniques that can be trained to learn or find relationships between inputs and outputs or to organize data so as to disclose so far unknown patterns or structures. It is usually used as a clustering/classification tool or used to find unknown relationships between a set of variables that describe a problem. The main property of the SOM is that it makes a nonlinear projection from a high-dimensional data space (one dimension per variable) on a regular, low-dimensional (usually 2D) grid of neurons, called units.
SOM is further processed using Ultsch method \cite{UmatUlts}, the Unified distance matrix (U-matrix), which uses SOM's codevectors (vectors of variables of the problem) as data source and generates a matrix where each component is a distance measure between two adjacent neurons. It allows us to visualize any multi-variated dataset in a two-dimensional display, so we can detect topological relations among neurons and infer about the input data structure. High values in the U-matrix represent a frontier region between clusters, and low values represent a high degree of similarities among neurons on that region, clusters.

SOMs (and U-Matrix) are usually applied for visualize natural structures in the data and their relations, as well as the natural groupings that could be among them. In addition, SOM makes easy the estimation of the variables that have more influence on these groupings. Other statistical and soft computing tools can also be used for this purpose, but since Kohonen's SOMs offers a visual way of doing it, it is much more intuitive, and takes advantage of the capabilities of the human brain as a pattern recognizer.
